Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7

### 2019-07-08 paper/ms.tex
minor

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page05.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Page 5: Cluster membership assessment diagnostics.}
		The star was considered a candidate cluster member by the source(s) listed under
		``Reference'', in this case \citet{dias_proper_2014}.
		The name used in the Dias catalog in this case was \texttt{264-025831}, a
		UCAC-4 identifier, which can be back-referenced to find that \citet{dias_proper_2014}
		assigned this star a
		membership probability in NGC 2546 of 98\%.
		The base catalog for the plots is chiefly that of \citet{Kharchenko_et_al_2013},
		due to its homogeneous parameter determination procedure (particularly for age).
		If a match to the \citet{Kharchenko_et_al_2013} catalog is found, then the remaining
		plots are populated.
		Top-left shows the parallax, with orange points sampled from the Gaia-DR2
		posterior, black points the other cluster members in the Kharchenko catalog,
		and the blue line the claimed Kharchenko parallax for the cluster.
		A large number of field contaminants are visible in this case.
		Top-right are the Gaia proper motions, where against black points are cluster
		members from Kharchenko, and the orange is the target star.
		Bottom-left is the HR diagram, and bottom-right are the on-sky positions.
		In the text,
		\texttt{N1sr2} is the number of $1\sigma$ cluster members claimed
		by \citet{Kharchenko_et_al_2013} within the cluster angular radius;
		$\log t$ is the base-10 logarithm of the age in years;
		\texttt{type} matches the type codes provided by \citet{Kharchenko_et_al_2013}.
		\label{fig:pg5}
	}
\end{figure*}

>>>>

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page05.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Page 5: Cluster membership assessment diagnostics.}
		The star was considered a candidate cluster member by the source(s) listed under
		``Reference'', in this case \citet{dias_proper_2014}.
		The name used in the Dias catalog in this case was \texttt{264-025831}, a
		UCAC-4 identifier, which can be back-referenced to find that \citet{dias_proper_2014}
		assigned this star a
		membership probability in NGC 2546 of 98\%.
		The base catalog for the plots is chiefly that of \citet{Kharchenko_et_al_2013},
		due to its homogeneous parameter determination procedure (particularly for age).
		If a match to the \citet{Kharchenko_et_al_2013} catalog is found, then the remaining
		plots are populated.
		Top-left shows the parallax, with orange points sampled from the Gaia-DR2
		posterior, black points the other cluster members in the Kharchenko catalog,
		and the blue line the claimed Kharchenko parallax for the cluster.
		A large number of field contaminants are visible in this case.
		Top-right are the Gaia proper motions, where against black points are cluster
		members from Kharchenko, and the orange is the target star.
    Bottom-left is the color-magnitude diagram, and bottom-right are
    the on-sky positions.  In the text,
		\texttt{N1sr2} is the number of $1\sigma$ cluster members reported
		by \citet{Kharchenko_et_al_2013} within the cluster angular radius;
		$\log t$ is the base-10 logarithm of the age in years;
		\texttt{type} matches the type codes provided by
    \citet{Kharchenko_et_al_2013};
    \texttt{K13Note} gives the description of the cluster from
    \citet{Kharchenko_et_al_2013}, if available.
		\label{fig:pg5}
	}
\end{figure*}
